\chapter{Overview}
\label{overview}

SOMHunter tool is just the main part of the whole set of software, analyses and publications related to it. The tool itself is the main "product" that could not exist without all the work done all around it. In this chapter, we'll briefly introduce all the parts to provide a somewhat solid view of the project as a whole.

\section{Generated Documentation}
The SOMHunter Core repository also contains a Doxygen documentation. You can generate it by yourself or use the pre-built one here\footnote{https://siret-junior.github.io/somhunter-core/}.

\section{Timeline}

\subsection{2019}
To understand the story better, let's start from the beginning. The first SOMHunter prototype started in 2019 and it was designed as a quite simple tool in its core features~\cite{kratochvil2020som}. It was implemented in the 3D engine\footnote{https://magnum.graphics/} with UI done in ImGUI\footnote{https://github.com/ocornut/imgui}. There were three main features that a user could employ. The first feature was the temporal text search based on the W2VV++ text to image model. Then we added an interactive browsing feature using the Bayesian relevance feedback algorithm. On top of that, we utilised possibilities of a self-organizing map (SOM) fitted on the relevance probability distribution for an overview display generation. 

\subsection{2020}
In January 2020 we participated using this version at VBS 2020 and we won. After the competition, we worked on a thorough analysis of our tool, as well as other competitors' tools~\cite{lokovc2021reign}. All this gave us valuable feedback on our work which might be useful to share with the world. Therefore we decided to port the tool's UI into a vanilla JS web application and we submitted it as an open-source version of our tool into ACM MM~\cite{kratochvil2020somhunter}. The open-source version was battle-tested in comparison with a team vitrivr\footnote{https://vitrivr.org/}. The results were published as a paper in IEEE MM~\cite{rosetto2021}. For the upcoming LSC 2020, we pushed the tool further~\cite{mejzlik2020somhunter}. Implementing the UI using React\footnote{https://reactjs.org/}, adding filters and the search history feature.


\subsection{2021}
In 2021, we started working on a large-scale evaluation of the users' relevance feedback behaviour. The aim was to model artificial users behaving like real ones and optimize the tool accordingly. We forked the tool's version to create a specific tool for data collecting for this --- we refer to this tool as SOMCollector\footnote{https://github.com/siret-junior/som-collector}. This is a stand-alone sealed software to allow future reproducibility of the experiments. We created an artificial user model which mimics the real users' selections using the collected data and prepared a simulation framework for further tool's optimizations. We refer to this framework as SOMHunter simulator\footnote{https://github.com/siret-junior/somhunter-simulator}. The effort concluded in journal publication~\cite{peska2021}. In parallel with this, we prepared the three-fold version of SOMHunter for the VBS 2021. Looking from the outside, three of our tools were competing at VBS 2021 --- SOMHunter, CollageHunter~\cite{lokovc2021video} and SOMHunter version from 2020. But all the tools were running the same tool under the hood, just with different configurations. This was the version after the whole restructuring of the project and switch to Ember.js\footnote{https://emberjs.com/} GUI implementation. Also, subframe querying with on-demand bitmap querying was added alongside many quality-of-life features.

We're getting to the end of the story. After VBS 2021 we again processed all the logs and did the analysis. For this, we created scripts\footnote{https://github.com/siret-junior/log-analyzer} that could be reused in the future. Again we participated in a post-VBS journal summarizing all the important takeaways. Moving on to LSC 2021 where we added support for the CLIP text to image model, created a dedicated ranking server as a service for this and merged bitmap with textual subframe querying. 

\subsection{Conclusion}
This chapter is just a very brief timeline of the SOMHunter, that emphasizes out some important points. At this point, you should have a solid understanding of how all the software pieces and publications match together with the SOMHunter Video Search Tool.

\pagebreak
\section{Publications}
This is the list of publication directly related to this project:
\begin{enumerate}
	\item \textbf{SOM-Hunter: Video browsing with relevance-to-som feedback loop.} Kratochvíl, M., Veselý, P., Mejzlík, F. and Lokoč, J., 2020, January. In International Conference on Multimedia Modeling (pp. 790-795). Springer, Cham.
	\item \textbf{SOMHunter: lightweight video search system with SOM-guided relevance feedback.} Kratochvíl, M., Mejzlík, F., Veselý, P., Soućek, T. and Lokoć, J., 2020, October. In Proceedings of the 28th ACM International Conference on Multimedia (pp. 4481-4484).
	\item \textbf{Is the Reign of Interactive Search Eternal? Findings from the Video Browser Showdown 2020.} Lokoč, J., Veselý, P., Mejzlík, F., Kovalčík, G., Souček, T., Rossetto, L., Schoeffmann, K., Bailer, W., Gurrin, C., Sauter, L. and Song, J., 2021.  ACM Transactions on Multimedia Computing, Communications, and Applications (TOMM), 17(3), pp.1-26.
	\item \textbf{SOMHunter for lifelog search.} Mejzlík, F., Veselý, P., Kratochvíl, M., Souček, T. and Lokoč, J., 2020, June. In Proceedings of the Third Annual Workshop on Lifelog Search Challenge (pp. 73-75).
	\item \textbf{SOMHunter V2 at Video Browser Showdown 2021.} Veselý, P., Mejzlík, F. and Lokoč, J., 2021, June. In International Conference on Multimedia Modeling (pp. 461-466). Springer, Cham.
	\item \textbf{Interactive Video Retrieval Evaluation at a Distance: Comparing Sixteen Interactive Video Search Systems in a Remote Setting at the 10th Video Browser Showdown} Silvan Heller; Viktor Gsteiger; Werner Bailer; Cathal Gurrin; Björn Þór Jónsson; Jakub Lokoc; Andreas Leibetseder; Frantisek Mejzlik; Ladislav Peska; Luca Rossetto; Konstantin Schall; Klaus Schoeffmann; Heiko Schuldt; Florian Spiess; Ly-Duyen Tran; Lucia Vadicamo; Patrik Vesely; Stefanos Vrochidis; Jiaxin Wu. Submitted to International Journal of Multimedia Information Retrieval 2021 November.
	\item \textbf{Evaluating a Bayesian-like Relevance Feedback Model with Text-to-Image Search Initialization} Peška, L., Vomlelová, M., Veselý, P., Škrhák, V. and Lokoč, J. Submitted to Multimedia Tools and Applications, 2021 October
	\item \textbf{SOMHunter for lifelog search.} Mejzlík, F., Veselý, P., Kratochvíl, M., Souček, T. and Lokoč, J., 2020, June. In Proceedings of the Third Annual Workshop on Lifelog Search Challenge (pp. 73-75).
	\item \textbf{On the User-Centric Comparative Remote Evaluation of Interactive Video Search Systems} Rossetto, Luca and Gasser, Ralph and Heller, Silvan and Parian-Scherb, Mahnaz and Sauter, Loris and Spiess, Florian and Schuldt, Heiko and Peška, Ladislav and Souček, Tomáš and Kratochvíl, Miroslav and Mejzlík, František and Veselý, Patrik and Lokoč, Jakub, in IEEE MultiMedia, vol. 28, no. 4, pp. 18-28, 1 Oct.-Dec. 2021, doi: 10.1109/MMUL.2021.3066779.
\end{enumerate}
